### 2018-01-04 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffAmer.tex
:art: Finished up all but one of Jeff's comments
:wrench: Removing the blue text after Marianito's approval

    and at $x = S^*(t)$, \textcolor{blue}{the following smooth pasting conditions are assumed to be satisfied}:

@@

        where $F$ and $g$ are the inverse Mellin transforms of $\tilde F$ and $\tilde g$, respectively. We have purposefully expanded the convolution term to its integral form as this makes the next step much easier to see. The point of introducing $\tilde F$ is because, upon inversion, this term itself is another convolution. That is,

@@

		To calculate $I_{2,a}$, we swap the integrals with respect to $z$ and $w$ and using the properties of the Dirac delta function gives us

@@

		\textcolor{blue}{Similarly to how we dealt with $I_{3,a}$}, we interchange the order of integration between $y$ and $z$, declare a substitution of $p = (zy)/S^*(u)$, then reverse the integration between $p$ and $y$. The result of these steps is

@@

		The integral $I_2$ follows a similar path for the lemmas and techniques used in deriving the analogous term with the American put. The lengthy calculations will be omitted, but the result is
        	\begin{equation}
        		\label{eqn:I2put}
        		I_2 = qx  \ds\sum\limits_{n=0}^{\infty}\int_t^T   \fr{(\lambda(u-t))^n}{n!} e^{n\mu_Y + n\sigma_Y^2/2} e^{(q+\lambda + \kappa\lambda)(u-t)} N\left( D_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u,
        	\end{equation}
	with $D_n$ defined in~\eqref{eqn:Dn}. 
	However, we will be providing the complete derivation and solution of $I_3$ as this term is rather complicated. As we will see, the result of $I_3$ will be a double integral which is more ideal to work with in comparison to a quadruple integral.

@@

        	For the American put option, we use~\eqref{eqn:amerPasting} and so have two conditions at our disposal. We will derive both of them. First we incorporate $v_{\text{a}}^{\text{put}}(S^*(t),t) = K - S^*(t)$ and we set $x = S^*(t)$ in~\eqref{eqn:amerJumpPut} to get
        	\begin{equation}
        		\label{eqn:inteqn1}
        		\begin{split}
        		K - S^*(t) = v_{\text{e}}^{\text{put}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_p\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        		\end{split}
        	\end{equation}
        	Eq.~\eqref{eqn:inteqn1} may initially appear to be a simple implicit equation for $S^*(t)$, but the hidden layer of complication lies in the function $g_p$ that contains the other unknown $v_{\text{a}}^{\text{put}}$. Thus if the American put option pricing problem for jump-diffusion processes were to be solved numerically, one would have to solve the~\eqref{eqn:amerJumpPut} and~\eqref{eqn:inteqn1} simultaneously. As we mentioned in the introduction, a scheme to solve this linked integral equation system was reported in~\cite{Chiarella2006}. Alternatively, we may use the other value-matching condition of $\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}(S^*(t),t) = -1$ to provide us with another integral equation for $S^*(t)$. Taking the partial derivative of~\eqref{eqn:amerJumpPut} with respect to $x$, we get
        	$$
        		\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}( x, t) = \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}\left(x,t\right) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{x}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        	$$
Then we evaluate this expression at $x = S^*(t)$ to find
		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			-1 &=  \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}
Similarly for the American call option and using~\eqref{eqn:amerPastingCall}, we would obtain the following:
		\begin{equation}
        		\label{eqn:inteqn3}
        		\begin{split}
        		S^*(t) - K = v_{\text{e}}^{\text{call}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_c\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u,
        		\end{split}
        	\end{equation}
 		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			1 &=  \fr{\pr v_{\text{e}}^{\text{call}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_c}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}

@@

        	\section{Approximate integro-differential equation to the free boundary for American options in jump-diffusion dynamics}
        	We could not solve the American option pricing problem along with its respective integral equations as demonstrated in the previous section due to the difficulty in determining $S^*$. Several numerical methods exist that have yielded quite positive results (e.g., see~\cite{Kallast2003} and~\cite{Chiarella2006}), but these often can be quite complex in implementation if minor details are omitted from the expositions. Thus in a similar manner to~\cite{Rodrigo2013} where an approximate ODE was found, we will derive an approximation for the free boundary $S^*$, except now we will be examining it in a jump-diffusion framework so the ODE will now be an integro-differential equation (IDE). The numerical results from~\cite{Rodrigo2013} for the standard diffusion dynamics in the asset price showed to be accurate when compared against widely accepted techniques for computing the American option value (e.g., the binomal method).

@@

	where we split the integral in $y$ at $y=1$ because this is the value that could determine if the quantity $z = yS^*(t)$ would place $v_{\text{a}}^{\text{put}}(z,t)$ in the continuation or exercise region. We have also given them temporary names $I_1$ and $I_2$ for ease of reference. We can immediately eliminate $I_2$ since it will decay to 0. This is because in this region, $y \in (1,\infty)$, and then this implies that $yS^*(t) > S^*(t)$. So the $z$ domain of $z \in (yS^*(t),\infty)$ by default is a subset of $z \in (S^*(t),\infty)$, which is precisely the continuation region. Hence $I_2$ will be 0 because 

@@

One of the traditional FDMs used in options pricing uses a few change of variables in order to change the PDE (or PIDE) to resemble the typical heat equation. Whilst this may be more elegant, we believe it is quite easy to lose track of the current variable space. Furthermore, it can be cumbersome to visualize these results because the original problem has been altered through these variable changes. Hence we will constrain our analysis to the original variables contained within the problem.

@@

\subsection{The approximate free boundary for an American put option}
Although we have derived an explicit approximation for $v_{\text{a}}^{\text{put}}(x,t)$ in~\eqref{eqn:amerputjumpLNApprox}, one obstacle remains: the second unknown $S^*$, the optimal exercise boundary. However, with the algorithm to solve~\eqref{eqn:SApproxPutLN}, we are able to obtain a complete profile of $S^*$ for the entire time domain that is specified. Ascertaining all the values of $S^*$ enables us to then solve~\eqref{eqn:amerputjumpLNApprox} as all the quantities will be known. A representation of $S^*$ from solving the approximate IDE~\eqref{eqn:SApproxPutLN} is given in Figure~\ref{fig:amerputFreeBoundary}. The plot for $S^*$ exhibits a similar behaviour as $S^*$ (i.e., in the standard diffusion model) in terms of monotonicity as was highlighted in~\cite{Rodrigo2013}.
	\begin{figure}[!h]
		\centering
		\includegraphics[scale=0.8]{figures/SfreePut.eps}
		\caption{The profile for $S^*$ from solving the approximate IDE~\eqref{eqn:SApproxPutLN} using $t=0$, $T=0.5$, $K = 5$, $r=0.05$, $q=0$, and $\sigma = 0.3$. The associated lognormal parameters are $\mu_Y = 0.9$, $\sigma_Y = 0.45$, and $\lambda = 0.1$.}
		\label{fig:amerputFreeBoundary}
	\end{figure}

@@

For the FDM, we use 101 spatial nodes and 501 temporal gridpoints. Consequently, this means we will also require 501 values of $S^*$ between $t=0$ and $t=0.5$. The domain of $S_0 \in [10^{-3},4K]$ will need to be divided into 100 equally-spaced subintervals to correspond to the 101 gridpoints used in the FDM. This is to ensure all resultant plots are consistent in terms of the input values used. For an American put option, we also require the following boundary conditions
	$$
		v_0^n = K, \quad v_I^n = 0, \quad \text{for all } n = 0,1,\ldots,N,
	$$
which correspond to the American put option at $S_0 \rightarrow 0$ and $S_0 \rightarrow \infty$ respectively for all time values in the domain. The option value curves are given in Figure~\ref{fig:amerputPlot} along with the absolute error between the two for the entire $S_0$ region. The MATLAB code for the FDM, the approximate IDE for $S^*$, and solving~\eqref{eqn:amerputjumpLNApprox} is available in the appendix with comments on how the code functions. Specifically, Appendix C.3 contains all that was used in this chapter.
	\begin{figure}[!h]
		\centering
		\subfigure[American put prices under jump-diffusion dynamics solved using the FDM scheme~\eqref{eqn:FDMPIDE} compared against~\eqref{eqn:amerputjumpLNApprox} with~\eqref{eqn:SApproxPutLN},~\eqref{eqn:freePutTLN} for the free boundary $S^*$. The price domain for the underlying asset is $(10^{-3},4K)$. The other financial parameters are $t=0$, $T=0.5$, $K = 5$, $r=0.05$, $q=0$, and $\sigma = 0.3$. \label{fig:amerputComp}]{\includegraphics[width=0.7\linewidth]{figures/amerputFDMApprox.eps}\hspace*{3pt}}
		\subfigure[The absolute error between the FDM and using~\eqref{eqn:SApproxPutLN} for the American put values in a jump-diffusion model. \label{fig:amerputError}]{\includegraphics[width=0.7\linewidth]{figures/amerputFDMApproxError.eps}
			}
		\caption{American put value plots from the FDM and approximate IDE system using~\eqref{eqn:amerputjumpLNApprox},~\eqref{eqn:SApproxPutLN}, and~\eqref{eqn:freePutTLN}. The domain for the asset price is once again $(10^{-3},4K)$.}
		\label{fig:amerputPlot}
\end{figure}

>>>>

    and at $x = S^*(t)$, \textcolor{black}{the following smooth pasting conditions are assumed to be satisfied}:

@@

        where $F$ and $g$ are the inverse Mellin transforms of $\tilde F$ and $\tilde g$, respectively. We have purposefully expanded the convolution term to its integral form as this makes the next step much easier to see. The point of introducing $\tilde F$ is \textcolor{black}{because, upon inversion,} this term itself is another convolution. That is,

@@

		To calculate $I_{2,a}$, we swap the integrals with respect to $z$ and $w$ and \textcolor{black}{using the properties of the Dirac delta function} gives us

@@

		\textcolor{black}{Similarly to how we dealt with $I_{3,a}$}, we interchange the order of integration between $y$ and $z$, declare a substitution of $p = (zy)/S^*(u)$, then reverse the integration between $p$ and $y$. The result of these steps is

@@

		The integral $I_2$ follows a similar path for the lemmas and techniques used in deriving the analogous term with the American put. The lengthy calculations will be omitted, but the result is
        	\begin{equation}
        		\label{eqn:I2put}
        		I_2 = qx  \ds\sum\limits_{n=0}^{\infty}\int_t^T   \fr{(\lambda(u-t))^n}{n!} e^{n\mu_Y + n\sigma_Y^2/2} e^{(q+\lambda + \kappa\lambda)(u-t)} N\left( D_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u,
        	\end{equation}
	with $D_n$ defined in~\eqref{eqn:Dn}. 
	However, we will be providing the complete derivation and solution of $I_3$ \textcolor{black}{as this term is rather complicated.} As we will see, the result of $I_3$ will be a double integral which is more ideal to work with in comparison to a quadruple integral.

@@

        	For the American put option, we use~\eqref{eqn:amerPasting} and so have two conditions at our disposal. We will derive both of them. First we incorporate $v_{\text{a}}^{\text{put}}(S^*(t),t) = K - S^*(t)$ and we set $x = S^*(t)$ in~\eqref{eqn:amerJumpPut} to get
        	\begin{equation}
        		\label{eqn:inteqn1}
        		\begin{split}
        		K - S^*(t) = v_{\text{e}}^{\text{put}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_p\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        		\end{split}
        	\end{equation}
        	Eq.~\eqref{eqn:inteqn1} may initially appear to be a simple implicit equation for $S^*(t)$, but the hidden layer of complication lies in the function $g_p$ that contains the other unknown $v_{\text{a}}^{\text{put}}$. Thus if the American put option pricing problem for jump-diffusion processes were to be solved numerically, one would have to solve the~\eqref{eqn:amerJumpPut} and~\eqref{eqn:inteqn1} simultaneously. As we mentioned in the introduction, a scheme to solve this linked integral equation system was \textcolor{black}{reported in~\cite{Chiarella2006}.} Alternatively, we may use the other value-matching condition of $\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}(S^*(t),t) = -1$ to provide us with another integral equation for $S^*(t)$. Taking the partial derivative of~\eqref{eqn:amerJumpPut} with respect to $x$, we get
        	$$
        		\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}( x, t) = \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}\left(x,t\right) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{x}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        	$$
Then we evaluate this expression at $x = S^*(t)$ to find
		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			-1 &=  \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}
Similarly for the American call option and using~\eqref{eqn:amerPastingCall}, we would obtain the following:
		\begin{equation}
        		\label{eqn:inteqn3}
        		\begin{split}
        		S^*(t) - K = v_{\text{e}}^{\text{call}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_c\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u,
        		\end{split}
        	\end{equation}
 		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			1 &=  \fr{\pr v_{\text{e}}^{\text{call}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_c}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}

@@

        	\section{Approximate integro-differential equation to the free boundary for American options in jump-diffusion dynamics}
        	We could not solve the American option pricing problem along with its respective integral equations as demonstrated in the previous section due to the difficulty in determining $S^*$. Several numerical methods exist that have \textcolor{black}{yielded quite positive results} (e.g., see~\cite{Kallast2003} and~\cite{Chiarella2006}), but these often can be quite complex in implementation if minor details are omitted from the expositions. Thus in a similar manner to~\cite{Rodrigo2013} where an approximate ODE was found, we will derive an approximation for the free boundary $S^*$, except now we will be examining it in a jump-diffusion framework so the ODE will now be an integro-differential equation (IDE). The numerical results from~\cite{Rodrigo2013} for the standard diffusion dynamics in the asset price \textcolor{black}{showed to be accurate} when compared against widely accepted techniques for computing the American option value (e.g., the binomal method).

@@

	where we split the integral in $y$ at $y=1$ because this is the value that \textcolor{black}{could} determine if the quantity $z = yS^*(t)$ would place $v_{\text{a}}^{\text{put}}(z,t)$ in the continuation or exercise region. We have also given them temporary names $I_1$ and $I_2$ for ease of reference. We can immediately eliminate $I_2$ since it will decay to 0. This is because in this region, $y \in (1,\infty)$, and then this implies that $yS^*(t) > S^*(t)$. So the $z$ domain of $z \in (yS^*(t),\infty)$ by default is a subset of $z \in (S^*(t),\infty)$, which is precisely the continuation region. Hence $I_2$ will be 0 because 

@@

\textcolor{black}{One of the traditional FDMs used in options pricing uses a few change of variables in order to change the PDE (or PIDE) to resemble the typical heat equation.} Whilst this may be more elegant, we believe it is quite easy to lose track of the current variable space. Furthermore, it can be cumbersome to visualize these results because the original problem has been altered through these variable changes. Hence we will constrain our analysis to the original variables contained within the problem.

@@

\subsection{The approximate free boundary for an American put option}
Although we have derived an explicit approximation for $v_{\text{a}}^{\text{put}}(x,t)$ in~\eqref{eqn:amerputjumpLNApprox}, one obstacle remains: the second unknown $S^*$, the optimal exercise boundary. However, with the algorithm to solve~\eqref{eqn:SApproxPutLN}, we are able to obtain a complete profile of $S^*$ for the entire time domain that is specified. Ascertaining all the values of $S^*$ enables us to then solve~\eqref{eqn:amerputjumpLNApprox} as all the quantities will be known. A representation of $S^*$ from solving the approximate IDE~\eqref{eqn:SApproxPutLN} is given in Figure~\ref{fig:amerputFreeBoundary}. The plot for $S^*$ exhibits a similar behaviour as $S^*$ (i.e., in the standard diffusion model) in terms of monotonicity as was highlighted in~\cite{Rodrigo2013}.
	\begin{figure}[!h]
		\centering
		\includegraphics[scale=0.6]{figures/SfreePut2.eps}
		\caption{The profile for $S^*$ from solving the approximate IDE~\eqref{eqn:SApproxPutLN} using $t=0$, $T=0.5$, $K = 5$, $r=0.05$, $q=0$, and $\sigma = 0.3$. The associated lognormal parameters are $\mu_Y = 0.9$, $\sigma_Y = 0.45$, and $\lambda = 0.1$.}
		\label{fig:amerputFreeBoundary}
	\end{figure}

@@

For the FDM, we use 101 spatial nodes and 501 temporal gridpoints. Consequently, this means we will also require 501 values of $S^*$ between $t=0$ and $t=0.5$. The domain of $S_0 \in [10^{-3},4K]$ will need to be divided into 100 equally-spaced subintervals to correspond to the 101 gridpoints used in the FDM. This is to ensure all resultant plots are consistent in terms of the input values used. For an American put option, we also require the following boundary conditions
	$$
		v_0^n = K, \quad v_I^n = 0, \quad \text{for all } n = 0,1,\ldots,N,
	$$
which correspond to the American put option at $S_0 \rightarrow 0$ and $S_0 \rightarrow \infty$ respectively for all time values in the domain. The option value curves are given in Figure~\ref{fig:amerputPlot} along with the absolute error between the two for the entire $S_0$ region. The MATLAB code for the FDM, the approximate IDE for $S^*$, and solving~\eqref{eqn:amerputjumpLNApprox} is available in the appendix with comments on how the code functions. Specifically, Appendix C.3 contains all that was used in this chapter.
	\begin{figure}[!h]
		\centering
		\subfigure[American put prices under jump-diffusion dynamics solved using the FDM scheme~\eqref{eqn:FDMPIDE} compared against~\eqref{eqn:amerputjumpLNApprox} with~\eqref{eqn:SApproxPutLN},~\eqref{eqn:freePutTLN} for the free boundary $S^*$. The price domain for the underlying asset is $(10^{-3},4K)$. The other financial parameters are $t=0$, $T=0.5$, $K = 5$, $r=0.05$, $q=0$, and $\sigma = 0.3$. \label{fig:amerputComp}]{\includegraphics[width=0.7\linewidth]{figures/amerputFDMApprox2.eps}\hspace*{3pt}}
		\subfigure[The absolute error between the FDM and using~\eqref{eqn:SApproxPutLN} for the American put values in a jump-diffusion model. \label{fig:amerputError}]{\includegraphics[width=0.7\linewidth]{figures/amerputFDMApproxError.eps}
			}
		\caption{American put value plots from the FDM and approximate IDE system using~\eqref{eqn:amerputjumpLNApprox},~\eqref{eqn:SApproxPutLN}, and~\eqref{eqn:freePutTLN}. The domain for the asset price is once again $(10^{-3},4K)$.}
		\label{fig:amerputPlot}
\end{figure}

### 2018-01-04 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffEuro.tex
:wrench: Added proof for F_n exists for n >= 2
:wrench: Removing the blue text after Marianito's approval

Analogous to \cite{Merton1976} and \cite{Frontczak2013}, we want to solve the problem (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). First, we assume that the function $v_\text{e} = v_\text{e}(x,t)$ denotes the European option with an underlying that is \textcolor{blue}{described by} jump-diffusion dynamics, and that is a solution to~(\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Applying the Mellin transform of $v_\text{e}$ with respect to $x$ to (\ref{eqn:PIDE}), \eqref{eqn:PIDEcondition}, we get

@@

\textcolor{blue}{As a short foreword, all derivations presented in this section are formal. Moreover, we will be assuming that the random variable $Y$ could belong to any family of distributions where $\E[Y]$ is finite and that $\E[Y^{-\xi}]$ is convergent.} To find $\J$, we can actually bypass the complex integral required for an inverse Mellin transform. From \eqref{eqn:JMellin}, we have

@@

@@

\textcolor{blue}{where $I$ is an arbitrary interval with endpoints $a$ and $b > a$; the interval can be open, half-closed or closed.} For example, a call option has payoff $\phi(x) = \max(x-K,0)$ which can be formulated as

@@

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since \textcolor{blue}{recent empirical studies (in particular, the tests performed in~\cite{Ramezani1998}) suggest a better model for the asset process involves the jumps following a double exponential distribution.} In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.

>>>>

Analogous to \cite{Merton1976} and \cite{Frontczak2013}, we want to solve the problem (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). First, we assume that the function $v_\text{e} = v_\text{e}(x,t)$ denotes the European option with an underlying that is \textcolor{black}{described by} jump-diffusion dynamics, and that is a solution to~(\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Applying the Mellin transform of $v_\text{e}$ with respect to $x$ to (\ref{eqn:PIDE}), \eqref{eqn:PIDEcondition}, we get

@@

\textcolor{black}{As a short foreword, all derivations presented in this section are formal. Moreover, we will be assuming that the random variable $Y$ could belong to any family of distributions where $\E[Y]$ is finite and that $\E[Y^{-\xi}]$ is convergent.} To find $\J$, we can actually bypass the complex integral required for an inverse Mellin transform. From \eqref{eqn:JMellin}, we have

@@

\textcolor{black}{Additionally, it is also possible to show that $F_n$ exists for all $n \geq 2$ provided use the aforementioned assumption that $\E{Y^{-\xi}}$ is finite and convergent. The details can be found in Appendix D.}

@@

\textcolor{black}{where $I$ is an arbitrary interval with endpoints $a$ and $b > a$; the interval can be open, half-closed or closed.} For example, a call option has payoff $\phi(x) = \max(x-K,0)$ which can be formulated as

@@

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since \textcolor{black}{recent empirical studies (in particular, the tests performed in~\cite{Ramezani1998}) suggest a better model for the asset process involves the jumps following a double exponential distribution.} In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.
